A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Fix conclusion

In terms of future work, we have 2 avenues of attack. First, we could use different dictionaries for different purposes. Many of the Python dictionaries are small, and their keysets never change. No one is adding a new built-in function in the near future.

Improve performance bottlenecks illustrated by benchmarks

>>>>

In terms of future work, we have 2 avenues of attack. First, we could use
different dictionaries for different purposes. Many of the Python dictionaries
are small, and their keysets never change. New built in functions are not added
during the runtime of the program and thus they could use perfect hashing.

Second, we could improve the performance bottlenecks illustrated by benchmarks.
These mainly consist of the extra time and memory bandwith and latency cost for
computing simple tabulation hashing.  If we optimize the hashing further
through more profiling, memory layout, and instruction order optimizing, we may
be able to achieve more real world gains.  We could also look into applying a
modifying of the perturbation trick currently used in Python for quadratic
probing.
